### 2015-02-27 icfp15-servo/browsers.tex
Various cleanup from first read

A URL identifies a resource to load.
This resource usually consists of HTML, which is then parsed and typically turned into a Document Object
Model (DOM) tree.
From a programming languages standpoint, there are several interesting aspects of the parser design
for HTML.
First, though the specification allows the browser to abort on a parse error\footnote{\url{https://html.spec.whatwg.org/multipage/#parsing}},
in practice browsers follow the recovery algorithms described in that specification precisely so that
even ill-formed HTML will be handled in an interoperable way across all browsers..
Second, due to the presence of the \lstinline[language=HTML]{<script>} tag, the token stream can be modified
during operation.
For example, the below example that injects an open tag for the header and comment blocks works in all modern browsers.
\begin{lstlisting}[language=HTML]
<html>
  <script>
  document.write(``<h'');
  </script>1>
  This is a h1 title

@@

That tree of elements, called the flow tree in Servo, is then processed to produce a set of display list items.
These list items are the actual graphical elements, text runs, etc. in their final on-screen positions.
The order in which these elements are displayed is well-defined by the standard\footnote{\url{http://www.w3.org/TR/CSS21/zindex.html#painting-order}}.

>>>>

A URL identifies a resource to load.
This resource usually consists of HTML, which is then parsed and typically turned into a Document Object
Model (DOM) tree.
From a programming languages standpoint, there are several interesting aspects of the parser design
for HTML.
First, though the specification allows the browser to abort on a parse error\footnote{\url{https://html.spec.whatwg.org/multipage/#parsing}},
in practice browsers follow the recovery algorithms described in that specification precisely so that
even ill-formed HTML will be handled in an interoperable way across all browsers.
Second, due to the presence of the \lstinline[language=HTML]{<script>} tag, the token stream can be modified
during operation.
For example, the below example that injects an open tag for the header and comment blocks works in all modern browsers.
\begin{lstlisting}[language=HTML]
<html>
  <script>
  document.write(``<h'');
  </script>1>
  This is a h1 title

@@

That tree of elements, called the \emph{flow tree} in Servo, is then processed to produce a set of \emph{display list} items.
These list items are the actual graphical elements, text runs, etc. in their final on-screen positions.
The order in which these elements are displayed is well-defined by the standard\footnote{\url{http://www.w3.org/TR/CSS21/zindex.html#painting-order}}.

### 2015-02-27 icfp15-servo/open.tex
Fix some typos and nits.
Various cleanup from first read

\paragraph{JavaScript object rooting.} Objects from the JavaScript
heap  are held onto by \Cplusplus{} object --- and sometimes vice-versa.
Today, all modern engines manually manage the boundary code to handle tracing
these objects, and this leads to leaking objects or, worse, freeing objects that
are still in use.
The lack of a typical garbage collector for these objects also means that cycles
between \Cplusplus{} and JavaScript need to be broken through ad-hoc means.

\paragraph{Integer overflow/underflow.} It is still an open problem
to provide optimized code that checks for overflow or underflow without
incurring significant performance penalties.
The current plan for Rust is to have debug-only checking of integer ranges
and for Servo to run debug builds against a test suite, but that may miss
scenarios that only occur in optimized builds.

>>>>

\paragraph{JavaScript object rooting.} Objects from the JavaScript
heap  are held onto by \Cplusplus{} objects --- and sometimes vice-versa.
Today, all modern engines manually manage the boundary code to handle tracing
these objects, and this leads to leaking objects or, worse, freeing objects that
are still in use.
The lack of a typical garbage collector for these objects also means that cycles
between \Cplusplus{} and JavaScript need to be broken through ad-hoc means.

\paragraph{Integer overflow/underflow.} It is still an open problem
to provide optimized code that checks for overflow or underflow without
incurring significant performance penalties.
The current plan for Rust is to have debug-only checking of integer ranges
and for Servo to run debug builds against a test suite, but that may miss
scenarios that only occur in optimized builds or that are not represented
by the test suite.

### 2015-02-27 icfp15-servo/rust.tex
Various cleanup from first read

Rust is a statically typed systems programming language most heavily inspired by the C
and ML families of languages~\cite{RUST}.
Like the C family of languages, it provides the developer control over the use of system
resources and facilities along with predictable performance.
In addition, it provides an ownership-based type system inspired by the region systems work in the
MLKit project~\cite{mlkit} and especially as implemented in the Cyclone project~\cite{cyclone}.
Unlike the ownership system in the Singularity project~\cite{singularity}, Rust allows APIs to
not only transfer ownership but also to temporarily \emph{borrow} values, significantly
reducing the number of region and ownership annotations required in large programs.
Rust also builds on ideas from typeclasses and type families in Haskell~\cite{haskell}.
Complete documentation and a language reference for Rust are available at: \url{http://doc.rust-lang.org/}.

>>>>

Rust is a statically typed systems programming language most heavily inspired by the C
and ML families of languages~\cite{RUST}.
Like the C family of languages, it provides the developer control over the use of system
resources and facilities along with predictable performance.
In addition, it provides an ownership-based type system inspired by the region systems work in the
MLKit project~\cite{mlkit} and especially as implemented in the Cyclone language~\cite{cyclone}.
Unlike the related ownership system in Singularity OS~\cite{singularity}, Rust allows APIs to
not only transfer ownership but also to temporarily \emph{borrow} values, significantly
reducing the number of region and ownership annotations required in large programs.
Rust also builds on ideas from typeclasses and type families in Haskell~\cite{haskell}.
Complete documentation and a language reference for Rust are available at: \url{http://doc.rust-lang.org/}.
